The Post-2007 Declining U.S. Birth Rates imply Significant Societal Shifts in the U.S.

### 2023-02-19 outputs/paper/paper.qmd
updates on the figures and tables

---
title: "The post 2007 is causing socialtal issue"
subtitle: "My subtitle if needed"
author: 
  - Saigth Kalaichelvam
  - Yougjo Kim
  - Joseph Chung
thanks: "Code and data are available at: https://github.com/UtopianYoungChung/Paper2.git"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper examines the causes of the steep decline in the US Birthrate since 2007. Firstly, the paper claims that certain demographic factors have contributed to the US birthrate decline since 2007. Secondly, the paper shows how other factors, such as economics or policy, do not exhibit dramatic change around the same time. Lastly, the paper shows strong evidence that the significant decrease in the US Birthrate during the post-2007 recession is related to the recent cohort of women."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

@@

Our data is of penguins (@fig-bills).

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

@@

Also bills and their average (@fig-billssssss). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work.)

```{r}
#| label: fig-billssssss
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

@@

>>>>

---
title: "The Post-2007 Declining U.S. Birth Rates imply Significant Societal Shifts in the U.S."
author: 
  - Sagith Kalaichelvam
  - Youngho Kim
  - Joseph Chung
thanks: "Code and data are available at: https://github.com/UtopianYoungChung/Paper2.git"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper explores several factors of the steep decline in birth rates in the United States between 2007 and 2020. The decline in U.S. birth rates offers some significant insights into U.S. society. Changes in birth patterns among recent young adult women moving through the childbearing age group can be directly related to the decline in birth rate from a purely statistical standpoint. In this paper, we decompose the decline in birth rates into between - and within - demographic groups. We then argue that any other economic, policy or social factor that has changed since 2007 does not contribute much to the decline. We also provide evidence that the steep drop in birth rates could be attributed to recent young adults' shifting interests. These shifting priorities represent changes in young adults' preferences regarding having children and aspirations for life. Resonating with the original paper, we conclude with a brief discussion of the implications of the declining birth rate in the United States and its impact on society as an entirety."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
library(knitr)
library(ggplot2)
```

@@

Figure 1. place it here with the Figure 1 from the Original paper (@fig-bills).

```{r}
#| label: fig-bills
#| fig-cap: Trend in US Birth Rates
#| echo: false

@@

Table 1. place it here with the table 1 from the Original paper

```{r}

```

Figure 2. place it here with the Figure 4 from the Original paper (@fig-billss).

```{r}
#| label: fig-billss
#| fig-cap: Relationship between Changes in Birth Rates 2004-2008 to 2014-2019
#| echo: false
#| fig-width: 8
#| fig-height: 4

@@

Figure 3. place it here with the Figure 2-a from the Original paper

```{r}
#| label: fig-billsss
#| fig-cap: Trends in Birth Rates by Population subgroup Five-year age group
#| echo: false
#| fig-width: 8
#| fig-height: 4

Figure 4. place it here with the Figure 5 from the Original paper
```{r}
#| label: fig-billssss
#| fig-cap: Children Ever Born by Mother's Age and Birth Cohort
#| echo: false
#| fig-width: 8
#| fig-height: 4

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()

```
